Determination of Magnitude and Intrinsic Flux of HD 227858 and HD 338931 from Landolt Standard SA 113475

### 2013-12-10 paper.tex
done

\documentclass{article}
\usepackage[latin1]{inputenc}
\usepackage{enumerate}
\usepackage{hyperref}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{tabularx}
\usepackage{amsmath}
\usepackage{amssymb}
\newcommand{\ket}[1]{\ensuremath{\left|#1\right\rangle}}
\newcommand{\bra}[1]{\ensuremath{\left\langle#1\right|}}
\newcommand{\braket}[2]{\ensuremath{\left\langle #1 \middle| #2 \right\rangle}}
\newcommand{\obar}[1]{\ensuremath{\overline{ #1 }}}
\hypersetup{colorlinks=true, urlcolor=blue, linkcolor=blue, citecolor=red}
\graphicspath{ {C:/Users/Evan/Desktop/} }
\title{Determination of Magnitude and Intrinsic Flux of HD 227858 and HD 338931 from Landholt Standard SA 113475}
\author{Evan Ott \\ UT EID: eao466}
\date{\today}
\setcounter{secnumdepth}{0}
%\usepackage[parfill]{parskip}
\begin{document}
\maketitle
\section{Introduction}
While the casual astrophotographer might only care about seeing as many stars as possible in an image, in academic astronomy,
we often want to have quantifiable data about stars, for example the magnitude (measure of brightness) of the star to compare it
to others, either in terms of total light or broken into sections of the electromagnetic spectrum by filters. Or, we might want to
have the flux (photon energy or number per area each second). However, besides having proper equipment, much calibration
must take place to account for all present factors - atmospheric extinction of photons travelling at different angles
through Earth's atmosphere, ever-present and never-present pixels in our sensor, absorption in mirrors and lenses, etc. Here, I work through calculating the magnitude and intrinsic flux (flux just outside the atmosphere) of stars HD 227858
and HD 338931 based on the Landhold Standard star SA 113475{\huge\cite{lanholt}}.

@@

\section{Methods}
Using the 16" telescope in Robert Lee Moore Hall at the University of Texas at Austin, I and my classmates used a 1024x1024 CCD imaging
system, coupled with a selection of Johnson-type filters for the B, V, R, and I parts of the spectrum. Parameters of the filters can be found in Table
\ref{table:filters}. After taking dark frame and flat frame images (to account for the CCD's inherent background response to temperature and
non-uniform sensitivity, respectively), we were able to use the IRAF suite of programs to isolate the count (in Arbitrary Data Units [ADU])
in the image due to photons from the stars of interest and the count associated with background light from other sources. These data
are found in Table \ref{table:Counts}.

@@

\begin{table}
\begin{center}
\begin{tabular}{c | c}
Filter & Intrinsic Magnitude \\
\hline
B & 11.362 \\
V &  10.304\\
R & 9.736\\
I & 9.208
\end{tabular}
\end{center}
\caption{Intrinsic magnitude of SA 113475 from \huge FIXME FIXME FIXME}
\label{table:SAmag}
\end{table}

@@

\begin{equation}
\label{eq:signalflux}
S_*=\frac{\Delta\nu{\obar{\Phi}}\frac{hc}{\lambda_0}}{g}n_\gamma=R\cdot n_\gamma
\end{equation}

@@

A handy consequence of Equation \ref{eq:signalflux} is that using the same filter and telescope setup for two
stars at the same exposure time gives $\frac{S_1}{S_2}=\frac{f_1}{f_2}$. As such, we can easly calculate the measured flux
of each target star for each filter (see Table \ref{table:fluxes}).

% $A=1280cm^2$ for the telescope, $t=30s$ for our dataset, and 
\begin{table}
\begin{center}
\begin{tabular}{c | c | c}
Star& Filter & Measured Flux\\
& &[erg cm$^{-2}$s$^{-1}$]\\
\hline
HD 227858 & B & 7.55E-10\\
HD 227858 & V & 1.24E-9\\
HD 227858 & R & 8.71E-10\\
HD 227858 & I & 2.53E-9\\
HD 338931 &B & 2.92E-9\\
HD 338931 &V & 4.66E-9\\
HD 338931 &R & 3.35E-9\\
HD 338931 & I & 1.04E-8\\
\end{tabular}
\caption{FIXME}
\label{table:fluxes}
\end{center}
\end{table}

@@

\begin{equation}
\label{eq:realflux}
F=f10^{\frac{kX}{2.5}}
\end{equation}

\begin{table}
\begin{center}
\begin{tabular}{c | c | c | c}
Star & Filter & Intrinsic Magnitude & Intrinsic Flux \\
& & & [erg cm$^{-2}$s$^{-1}$] \\
\hline
HD 227858 & B & 11.295 & 1.29E-8\\
HD 227858 & V & 10.469  & 6.30E-9\\
HD 227858 & R & 10.053 & 3.88E-9\\
HD 227858 & I  & 8.623 & 1.26E-8\\
HD 338931 & B & 9.766 & 5.69E-8\\
HD 338931 & V & 9.009  & 2.47E-8\\
HD 338931 & R & 8.576 & 1.54E-8\\
HD 338931 & I & 7.018 & 5.38E-8\\
SA 113475 & B & 11.362 & 1.13E-8\\
SA 113475 & V & 10.304 & 7.14E-9\\
SA 113475 & R  & 9.736 & 5.10E-9\\
SA 113475 & I  & 9.208 & 7.15E-9\\
\end{tabular}
\caption{FIXME}
\label{table:realflux}
\end{center}
\end{table}

\section{Analysis}

\section{Conclusion}

\begin{thebibliography}{9}

>>>>

\documentclass{article}
\usepackage[latin1]{inputenc}
\usepackage{enumerate}
\usepackage{hyperref}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{tabularx}
\usepackage{amsmath}
\usepackage{amssymb}
\newcommand{\ket}[1]{\ensuremath{\left|#1\right\rangle}}
\newcommand{\bra}[1]{\ensuremath{\left\langle#1\right|}}
\newcommand{\braket}[2]{\ensuremath{\left\langle #1 \middle| #2 \right\rangle}}
\newcommand{\obar}[1]{\ensuremath{\overline{ #1 }}}
\hypersetup{colorlinks=true, urlcolor=blue, linkcolor=blue, citecolor=red}
\graphicspath{ {C:/Users/Evan/Desktop/} }
\title{Determination of Magnitude and Intrinsic Flux of HD 227858 and HD 338931 from Landolt Standard SA 113475}
\author{Evan Ott \\ UT EID: eao466}
\date{\today}
\setcounter{secnumdepth}{0}
%\usepackage[parfill]{parskip}
\begin{document}
\maketitle
\section{Introduction}
While the casual astrophotographer might only care about seeing as many stars as possible in an image, in academic astronomy,
we often want to have quantifiable data about stars, for example the magnitude (measure of brightness) of the star to compare it
to others, either in terms of total light or broken into sections of the electromagnetic spectrum by filters. Or, we might want to
have the flux (photon energy or number per area each second). However, besides having proper equipment, much calibration
must take place to account for all present factors - atmospheric extinction of photons travelling at different angles
through Earth's atmosphere, ever-present and never-present pixels in sensors, absorption in mirrors and lenses, etc. Here, I work through calculating the magnitude and intrinsic flux (flux just outside the atmosphere) of stars HD 227858 (see Figure \ref{fig:hd2})
and HD 338931 (see Figure \ref{fig:hd3}) based on the Landolt Standard star SA 113475 (see Figure \ref{fig:sa})\cite{landolt}.

\begin{figure}[h]
\centering
\includegraphics[scale=.75]{hd2.jpg}
\caption{\label{fig:hd2} HD 227585 and surrounding stars, colored by linear scale in number of counts per pixel.}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[scale=.75]{hd3.jpg}
\caption{\label{fig:hd3} HD 338931 and surrounding stars, colored by linear scale in number of counts per pixel.}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[scale=.75]{sa1.jpg}
\caption{\label{fig:sa} Landolt Standard star SA 113475 and surrounding stars, colored by linear scale in number of counts per pixel.}
\end{figure}

@@

\section{Methods}
Using the 16" telescope at Robert Lee Moore Hall at the University of Texas at Austin, I and my classmates used a 1024x1024 CCD imaging
system, coupled with a selection of Johnson-type filters for the B, V, R, and I parts of the spectrum to analyse HD 227858 and HD 338931. Parameters of the filters can be found in Table
\ref{table:filters}. After taking dark frame and flat frame images (to account for the CCD's inherent background response to temperature and
non-uniform sensitivity, respectively), we were able to use the IRAF suite of programs to isolate the count (in Arbitrary Data Units [ADU])
in the image due to photons from the stars of interest and the count associated with background light from other sources. These data
are found in Table \ref{table:Counts}.

@@

\begin{table}
\begin{center}
\begin{tabular}{c | c}
Filter & Intrinsic Magnitude \\
\hline
B & 11.362 $\pm$ 0.0006\\
V &  10.304 $\pm$ 0.0004\\
R & 9.736 $\pm$ 0.0006\\
I & 9.208 $\pm$ 0.0008
\end{tabular}
\end{center}
\caption{Intrinsic magnitude of SA 113475 from Landolt \cite{landolt}.}
\label{table:SAmag}
\end{table}

@@

\begin{equation}
\label{eq:signalflux}
S_*=\frac{\Delta\nu{\obar{\Phi}}t{\obar{f_*}}A}{g}=\frac{\Delta\nu{\obar{\Phi}}\frac{hc}{\lambda_0}}{g}n_\gamma=R\cdot n_\gamma
\end{equation}

@@

A handy consequence of Equation \ref{eq:signalflux} is that using the same filter and telescope setup for two
stars with the same exposure time gives $\frac{S_1}{S_2}=\frac{f_1}{f_2}$. As such, we can easly calculate the measured flux
of each target star for each filter (see Table \ref{table:fluxes}).

\begin{table}
\begin{center}
\begin{tabular}{c | c | c}
Star& Filter & Measured Flux\\
& &[erg cm$^{-2}$s$^{-1}$]\\
\hline
HD 227858 & B & 7.55E-10\\
HD 227858 & V & 1.24E-9\\
HD 227858 & R & 8.71E-10\\
HD 227858 & I & 2.53E-9\\
HD 338931 &B & 2.92E-9\\
HD 338931 &V & 4.66E-9\\
HD 338931 &R & 3.35E-9\\
HD 338931 & I & 1.04E-8\\
\end{tabular}
\caption{Measured flux of target stars based on the measured flux of SA 113475.}
\label{table:fluxes}
\end{center}
\end{table}

@@

\begin{equation}
\label{eq:realflux}
F=f\cdot10^{kX/2.5}
\end{equation}

\begin{table}
\begin{center}
\begin{tabular}{c | c | c | c}
Star & Filter & Intrinsic Magnitude & Intrinsic Flux \\
& & & [erg cm$^{-2}$s$^{-1}$] \\
\hline
HD 227858 & B & 11.295 & 1.29E-8\\
HD 227858 & V & 10.469  & 6.30E-9\\
HD 227858 & R & 10.053 & 3.88E-9\\
HD 227858 & I  & 8.623 & 1.26E-8\\
HD 338931 & B & 9.766 & 5.69E-8\\
HD 338931 & V & 9.009  & 2.47E-8\\
HD 338931 & R & 8.576 & 1.54E-8\\
HD 338931 & I & 7.018 & 5.38E-8\\
SA 113475 & B & 11.362* & 1.13E-8\\
SA 113475 & V & 10.304* & 7.14E-9\\
SA 113475 & R  & 9.736* & 5.10E-9\\
SA 113475 & I  & 9.208* & 7.15E-9\\
\end{tabular}
\caption{Final results (minus uncertainties) for the magnitude and flux of each target star in each filter band. *Values are from \cite{landolt}.}
\label{table:realflux}
\end{center}
\end{table}

\section{Analysis}
From Equation \ref{eq:targetstar}, we can calculate the uncertainty in target star magnitudes, target star fluxes, and atmospheric extinction coefficients.
For general function $f=f(x_1, x_2, ..., x_n)$, we expect: $$\sigma_f^2=\Sigma_{i=1}^{n}(\partial_{x_i}f(x_1, x_2, ..., x_n)\sigma_{x_i})^2$$
Thus for magnitudes of target stars, we have:
\begin{equation*}
\sigma_{m_1}^2=\sigma_{m_2}^2+6.25\left(\left(\frac{\sigma_{t_1}}{t_1}\right)^2+\left(\frac{\sigma_{S_1}}{S_1}\right)^2
+\left(\frac{\sigma_{t_2}}{t_2}\right)^2+\left(\frac{\sigma_{S_2}}{S_2}\right)^2\right) + 4k^2\sigma_X^2+\sigma_k^2(X_1-X_2)^2
\end{equation*}
For extinction coefficients, we have:
\begin{equation*}
\sigma_k^2/6.25=\left(\frac{\sigma_{t_1}}{t_1}\right)^2+\left(\frac{\sigma_{S_1}}{S_1}\right)^2
+\left(\frac{\sigma_{t_2}}{t_2}\right)^2+\left(\frac{\sigma_{S_2}}{S_2}\right)^2
+\log_{10}\left(\frac{S_1t_2}{S_2t_1}\right)(X_1-X_2)^{-2}(\sigma_{X_1}^2+\sigma_{X_2}^2)
\end{equation*}
For flux, we arrive at:
\begin{equation*}
\sigma_{f_1}^2=f_1^2\left[
\frac{\sigma_{f_2}^2}{f_2^2}+\frac{\ln10}{6.25}\left(
\sigma_{m_1}^2+\sigma_{m_2}^2+\sigma_k^2(X_1-X_2)^2+k^2(\sigma_{X_1}^2+\sigma_{X_2}^2)
\right)
\right]
\end{equation*}
And finally, for system response, we know $nR=S$ and $n=\frac{fAt\lambda_0}{hc}$, so we arrive at
\begin{align*}
\sigma_R^2=&\frac{\sigma_S^2}{n^2}+\frac{S^2\sigma_n^2}{n^4} \\
\sigma_n^2=&n^2\left(\frac{\sigma_f^2}{f^2}+\frac{\sigma_A^2}{A^2}+\frac{\sigma_t^2}{t^2}\right)\\
\sigma_S^2=&S
\end{align*}
For our known uncertainties, we have the uncertainty in magnitude of SA 113475 from the literature, $t=30s$,
$\sigma_t\approx0.001s$,
$A=1280cm^2$,
$\sigma_A\approx.5\textrm{cm}^2$,
$\sigma_X\approx0.01$, and $\sigma_S^2=S$. This and data above are sufficient to calculate the error in $k$ for each filter,
which can then be used to calculate the error in magnitudes and flux (each by starting with known error in measurement of stars).

\section{Conclusion}
With magnitude of HD 227858 having an accepted value of $B=11.20\pm0.05,~V=10.76\pm0.06$ \cite{hd2}, with the observed value from the RLM
telescope for $B$ within two standard deviations but $V$ is not within 4.5$\sigma_V$, surely there must be unaccounted for sources of error,
potentially including human error in processing the raw data or collecting the original images. To be fair, without full calculation
of error in my measurement which I have detailed but not completed, it is entirely possible that the standard error on my measurement
is sufficiently large as to account for this difference due simply to uncertainty. However, with accepted values $B=9.72,~V=9.14$\cite{hd3}
for HD 338931, the observed values are within 1\% and 1.5\% respectively (no error given in \cite{hd3}), it would appear likely that
the observed values here are indeed consistent.

This shows that although the RLM telescope is in the heart of air- and light-polluted Austin, Texas and is miniscule compared to UT's own
telescopes at the McDonald Observatory, real, workable data is attainable with the right mathematical framework. Furthermore, continuing
to take measurements of additional stars would help in calibrating results (rather than basing the extinction coefficient for a filter
on two reduced samples).

\begin{thebibliography}{9}
\bibitem{hd2} H\o{t}, E., et al. ``The Tycho-2 catalogue of the 2.5 million brightest stars''. {\emph{Astronomy and Astrophysics}} v.355, p.L27-L30. (2000)
\bibitem{landolt} Landolt, A.U. ``{\emph{UBVRI}} Photometric Standard Stars Around the Celestial Equator: Updates and Additions''. {\emph{The
Astronomical Journal}}. {\bf{137}} 4186. (2009) \url{http://iopscience.iop.org/1538-3881/137/5/4186}
\bibitem{hd3} Reed, B.C. ``Catalog of Galactic OB Stars''. {\emph{The Astronomical Journal}}. {\bf{125}} 2531. (2003)
\url{http://iopscience.iop.org/1538-3881/125/5/2531/}
